---
title: "Simple document"
author: "Matariya Rattanapan"
date: 2025-09-09
output: html_document
---

I'm an R Markdown document! 

```{r echo = TRUE, message = FALSE}
library(tidyverse)
```


# Section 1

Here's a **code chunk** that samples from 
a _normal distribution_:

```{r}
samp = rnorm(100)
length(samp)
```

# Section 2

I can take the mean of the sample, too!
The mean is `r mean(samp)`.

# Section 3

This is where I'm going to talk about code chunks.

```{r eval = FALSE}
samp = rnorm(100)
length(samp)
```

Let's make a dataframe.

```{r}
example.df = 
  tibble(
    vec_numeric = 1:4,
    vec_char = c("my", "name", "is", "jeff"),
    vec_factor = factor(c("male", "male", "female", "female"))
  )
```

I'll create a new dataframe.
```{r}
new_df =
  tibble(
    x = rnorm(100),
    y = 1 + 2 * x + rnorm(100)
  )
```

Let's make a plot and see how cool

```{r}
plot_df = 
  tibble(
    x = rnorm(1000, mean = 1, sd = 0.5),
    y = 1 + 2 * x + rnorm(1000)
  )

plot_df

ggplot(plot_df, aes(x=x)) + geom_histogram()
ggplot(plot_df, aes(x=x, y=y)) + geom_point()
```

# Learning Assessment

```{r}
la_df = 
  tibble(
    numeric_samp = rnorm(500, mean = 1),
    greater_0 = numeric_samp > 0,
    abs_value_samp = abs(numeric_samp)
  )

ggplot(la_df, aes(x= abs_value_samp)) + geom_histogram()
```

To use inline code, I would do something like: "The sample size in the new dataframe is `r nrow(la_df)`."

Something more complex is "The mean of my new variable is `r mean(pull(la_df, abs_value_samp))`."

# Let's look at formatting

ll of this is markdown formatting

`italic` or _italic_
